Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-08-10 writeup/gz_hubble_data.tex
Figure 10 has five quantiles, not four. Closes #184.

For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
cannot be confidently assigned, the \emph{range} of debiased values is
estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
\ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
values for any given observed \ffeatures{} value, again as a function of
surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, the spread of
intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures{} is computed.
The range of intrinsic values is defined as the inner 80\% of the data,
represented by the orange bars in Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which
cannot be directly debiased by the $\zeta$ method, these ranges are used to
denote the upper and lower limits on the expected values \ffeaturesrest{} as a
function of the observed \ffeatures.

>>>>

For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
cannot be confidently assigned, the \emph{range} of debiased values is
estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
\ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
values for any given observed \ffeatures{} value, again as a function of
surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
we compute the spread of
intrinsic values of \ffeaturesrest{} for five quantiles of observed \ffeatures{}
(corresponding to the ``clean'' thresholds used in prior GZ publications).
The range of intrinsic values for GZH is defined as the inner 80\% of the data,
represented by the orange bars in Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which
cannot be directly debiased by the $\zeta$ method, these ranges are used to
denote the upper and lower limits on the expected values \ffeaturesrest{} as a
function of the observed \ffeatures.
